### 2019-01-03 taco/tex/motivation.tex
Add taco
revise some errors
Major revision

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.

\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

@@

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
For a cluster with $n$ slots, the number of tasks should be $n \times k (k \geq 1)$. 
For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism. 
Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).

Since the shuffle data becomes available as soon as the end of a task's execution, 
and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data. 
To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

>>>>

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/util}
		\caption{Original Spark}
		\label{fig:util}
	\end{subfigure}
	\begin{subfigure}[b]{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/scache_util}
		\caption{Spark With SCache}
		\label{fig:scache_util}
	\end{subfigure}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
\end{figure*}

@@

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
% For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism. 
% Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
Since the shuffle data becomes available as soon as the end of a task's execution, 
and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

% Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data. 
To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

### 2019-01-03 taco/tex/relatedwork.tex
Major revision

{\color{blue}
\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers. The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers.

However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
}

>>>>

{\color{blue}
\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job abd combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
}
